Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-08 analysis/paper/paper.Rmd
try different prior but not much difference, add sentences to statistics

---
title: "Bayesian exponential random graph modelling of KWL Burial network"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

We use burial data from different time periods at Kiwulan and consider the effects of both exogenous and endogenous factors that could provide meaningful explanation of the characteristics of burial network and tendency of burials correlate with each other. To be specific, our purpose is to understand the underlying mechanisms of the network structures and how the relationship influence on the pattern of accumulation of wealth during different foreign contact periods. We focus on connectivity, clusters, centralization, and homophily among those burials that could reflect the social relations between individuals guided by social structures.Previous studies have shown that there are some evidence of social inequality observed from Kiwulan but the degree over time and causes remain unclear. To answer our question for the shifts in social inequality to a more wealth differentiation during and after the arrival of the foreign presences, we hypothesize:

@@

We used ergm package in R for the model specification. Every term in an ERGM must have an associated algorithm for computing its value for network [@Morris2008]. The terms we selected for nwtwork specification include:

@@

@@

ggraph(relation_tidy_pre) +
  geom_edge_link() +
  geom_node_point() +
  theme_graph()

ggraph(relation_tidy_pre, layout = "graphopt") +
  geom_node_point() +
  geom_edge_link(aes(width = common_counts), alpha = 0.8) +
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_text(aes(label = burial_label), repel = TRUE) +
  labs(edge_width = "common item") +
  theme_graph()
```

@@

```{r Bayesian-ERGMs}
# Specify a prior distribution: normal distribution (low density and high transitivity)
prior.mean <- c(-3, 0, 0, 1, 0) # prior mean corresponds to mean for each parameter
# follow Alberto Caimo et al. (2015) hospital example
prior.sigma <- diag(3, 5, 5) # covariance matrix structure
# where the dimension d corresponds to the number of parameters, 𝜇 is mean vector and Σprior is a d × d covariance matrix.

@@

@@

inline code `r x` example

>>>>

---
title: "Bayesian exponential random graph modelling of KWL Burial network"
author:
  - Author One
  - Author Two
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

We use burial data from different time periods at Kiwulan and consider the effects of both exogenous and endogenous factors that could provide meaningful explanation of the characteristics of burial network and tendency of burials correlate with each other. To be specific, our purpose is to understand the underlying mechanisms of the network structures and how the relationship influence on the pattern of accumulation of wealth during different foreign contact periods. We focus on connectivity, clusters, centralization, and homophily among those burials that could reflect the social relations between individuals guided by social structures. Previous studies have shown that there are some evidence of social inequality observed from Kiwulan but the degree over time and causes remain unclear. To answer our question for the shifts in social inequality to a more wealth differentiation during and after the arrival of the foreign presences, we hypothesize:

@@

We used ergm package in R for the model specification. Every term in an ERGM must have an associated algorithm for computing its value for network [@Morris2008]. The terms we selected for network specification include:

@@

4. nodematch: uniform homophily that refers to the similarity of connected nodes. A statistics that counts the number of edges between nodes sharing the same covariate value or characteristics.

@@

# plot
ggraph(relation_tidy_pre, layout = "graphopt") +
  geom_node_point() +
  geom_edge_link(aes(width = common_counts), alpha = 0.8) +
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_text(aes(label = burial_label), repel = TRUE) +
  labs(edge_width = "common item") +
  theme_graph()
```

@@

```{r Bayesian-ERGMs}
# Specify a prior distribution: normal distribution (low density and high transitivity)
# need to observe the graph and select suitable prior 
prior.mean <- c(1, 0, 0, 3, 0) # prior mean corresponds to mean for each parameter
# follow Alberto Caimo et al. (2015) hospital example
prior.sigma <- diag(3, 5, 5) # covariance matrix structure
# where the dimension d corresponds to the number of parameters, 𝜇 is mean vector and Σprior is a d × d covariance matrix.

@@

The plots from left to right show estimated marginal posterior densities, trace plots, and autocorrelation plots.

@@
